\section{Introduction}

IoT dashboards are an operational interface rather than a passive sink for telemetry. When every sensor update is forwarded immediately, the browser-facing path inherits bursty arrival patterns, repeated redraws, and abrupt visibility gaps during connectivity faults. For an operator monitoring a live deployment, the relevant failure mode is therefore loss of interpretability at the dashboard, not simply loss of transport efficiency. That distinction is especially important when the impairment lies on the final gateway-to-dashboard hop, where the broker can remain healthy while the rendered view becomes erratic.

This paper studies that dashboard-facing problem in the path \texttt{dataset replay $\rightarrow$ MQTT broker $\rightarrow$ smart gateway $\rightarrow$ WebSocket dashboard}. The central question is not whether a gateway can reduce traffic in the abstract, but whether it can trade immediacy for operator-visible stability in a controlled and measurable way. In this setting, stability means a paced downstream rendering stream with predictable behavior during outage and recovery, while freshness means how old the visible state is when the dashboard renders it.

Agrasandhani addresses this question with a gateway that can batch sensor updates, compact each batch to the latest reading per sensor, optionally adapt its batch window, and expose last-known-good state with explicit age semantics. The empirical story that emerges is intentionally narrower than a generic optimization claim. The strongest measured effect is a large reduction in downstream frame cadence under last-hop impairment, especially during outage and recovery. That effect does not imply lower payload-byte volume, and it is accompanied by higher display latency and older visible state.

The paper makes three bounded contributions:
\begin{itemize}[leftmargin=*]
  \item It quantifies the primary gateway trade-off under last-hop impairment: smart variants sharply reduce downstream frame cadence and produce a steadier dashboard stream, but they increase end-to-end latency.
  \item It distinguishes continuity from freshness by showing that last-known-good state improves visible outage behavior while increasing the age of the displayed data.
  \item It reports negative and mixed results explicitly: downstream payload bytes do not decrease in this setup, the adaptive controller does not materially outperform fixed-window batching, and the measured benefit beyond batching alone is limited.
\end{itemize}

Specifically, the paper tests whether gateway-side pacing and retained-state semantics improve dashboard stability under last-hop impairment, and what they cost in latency, freshness, and payload volume.
