\section{Discussion and Threats to Validity}

The final evidence supports a narrow systems interpretation. The gateway is most useful when the design objective is dashboard continuity under last-hop impairment rather than minimum per-message latency. The dominant mechanism is pacing: the gateway emits far fewer downstream frames and therefore makes the rendered stream easier to follow. V4 extends that behavior by preserving last-known-good state through outage. The trade-off is explicit throughout the results: display latency rises, visible age rises, and downstream payload bytes do not fall. The contribution is therefore not generic communication efficiency, but a controlled reshaping of operator-visible behavior under impairment.

\subsection{Threats to Validity}

Several limits bound the generality of the result. First, the main evidence comes from bounded Intel and AoT slices executed on a local, machine-scale testbed; the results should not be read as a deployment-wide claim about larger workloads or different gateway placements. Second, the reported downstream metrics are proxy-side measurements on the gateway-to-dashboard hop. That boundary is appropriate for a dashboard-facing question, but it does not establish a generic broker or WAN result. Third, the QoS observations are setup-specific: the local broker configuration produces zero observed exact duplicate drops, so the QoS discussion remains descriptive rather than universal. Finally, missing-update attribution is often unavailable once aggregation changes proxy and gateway frame counts, which limits fine-grained causal claims about every omitted dashboard update. These limits do not invalidate the primary result, but they constrain it to a dashboard-facing, last-hop impairment study.

\Needspace{10\baselineskip}
\section{Conclusion}

Agrasandhani demonstrates that a smart gateway can make an IoT dashboard materially steadier under last-hop impairment by sharply reducing downstream frame cadence and, in V4, preserving visible state through disruption. The same evaluation also makes the costs explicit: higher display latency, older visible state, no blanket downstream byte reduction, and no material gain from the tested adaptive controller. Under the replicated workloads studied here, gateway-side pacing is therefore best understood as a continuity mechanism for impaired dashboard paths rather than as a universal throughput optimization.
