\section{Experimental Evaluation}

% [proposal] Research questions
We structure the evaluation of Agrasandhani around the following research questions (RQs), which directly reflect the failure modes of naive forwarding and the design goals of smart aggregation under MQTT and degraded networks. \textbf{RQ1 (Bandwidth vs. timeliness):} How much does hybrid batching and latest-per-sensor compaction reduce gateway-to-dashboard bandwidth compared to forwarding every message, and what latency/tail-latency cost does this introduce under normal and bursty loads? \textbf{RQ2 (Reliability-induced duplicates):} Under MQTT QoS~1 (``at least once'' delivery), which may introduce duplicate deliveries via retransmissions \cite{mqtt311}, how effective is message-ID-based deduplication at reducing duplicate-induced overhead while preserving correct state at the dashboard? \textbf{RQ3 (Robustness under impairments):} Under deterministic last-hop impairments (bandwidth caps, loss, delay, jitter, and short outages) injected with Linux traffic control (e.g., \texttt{tc netem}) \cite{jurgelionis2011_netem_empirical}, which gateway variant best maintains dashboard stability as measured by data loss, update jitter, and tail latency? \textbf{RQ4 (User-visible freshness):} How does last-known-good caching with an explicit age indicator and TTL affect the freshness distribution (age of displayed values) during and after impairments, and what trade-offs emerge between reduced communication and increased staleness? \textbf{RQ5 (Ablation and attribution):} Across an ablation ladder (V0--V4), which individual mechanism (batching, compaction, adaptive publish rate, or last-known-good semantics) accounts for the largest improvements for each metric?

\subsection{Evaluation Setting}
% [proposal] Evaluation plan
We will evaluate Agrasandhani using an end-to-end local testbed consisting of (i) a Python/asyncio sensor simulator publishing JSON messages \texttt{\{sensor\_id, msg\_id, ts\_sent, value, type\}} to an MQTT broker, (ii) a smart gateway subscribing to the raw topic and publishing aggregated updates to an output topic, and (iii) a lightweight dashboard backend that subscribes to aggregated updates and streams them to a browser UI over WebSockets. The primary comparison is an ablation ladder of gateway variants: V0 (naive forward-every-message), V1 (hybrid batching with flush every $T$ ms or $K$ messages), V2 (V1 plus two-stage deduplication and latest-per-sensor compaction), V3 (V2 plus adaptive publish rate by adjusting $T$ based on publish health signals such as send time and queue backlog), and V4 (V3 plus last-known-good dashboard semantics with explicit age and TTL). For each variant, we will run MQTT under QoS~0 and QoS~1 to expose reliability/duplicate effects; MQTT v3.1.1 defines QoS~0 as ``at most once'' and QoS~1 as ``at least once'' delivery \cite{mqtt311}. We will sweep workload intensity by varying the number of simulated sensors and their rate schedule (including deterministic burst phases), while using a mixed sensor model (slowly changing versus spiky values) to reflect heterogeneous update dynamics. To stress the user-visible last hop, we will inject deterministic, repeatable network degradations primarily on the gateway-to-dashboard path using Linux traffic control (bandwidth caps plus \texttt{tc netem} for loss, delay, jitter, and outage-like disruptions) \cite{jurgelionis2011_netem_empirical}. Each condition will be executed for multiple trials (e.g., 2--3) with fixed random seeds to support repeatability. We will report end-to-end latency from \texttt{ts\_sent} to dashboard receipt/display (including p50/p95/p99), message rate (msgs/sec) at each stage, bandwidth usage (bytes/sec) on the gateway egress, and data loss defined via missing/late updates inferred from per-sensor \texttt{msg\_id} sequences. In addition, we will measure user-visible stability via update jitter (inter-arrival variance) and freshness via the age distribution of displayed values (with TTL-based staleness marking), enabling a rigorous characterization of the trade-offs between communication reduction, timeliness, and dashboard robustness under degraded networks.

% \subsection{Evaluation Results}
% Present the results of individual research questions in this subsection. Use tables/figures to present the results. You need to discuss discuss your observations and speculate the reasons for observations. 