\section{Related Work}

% [proposal] Related work (2--3 sentences each)

\noindent\textbf{Edge/fog data reduction and aggregation.}
Pioli et al.\ provide a systematic mapping of data reduction solutions performed at the IoT edge, categorizing techniques such as filtering, aggregation, and adaptation, and emphasizing the need for rigorous, comparative evaluation across workloads and environments \cite{pioli2022_edge_data_reduction_mapping}. This motivates our focus on gateway-side reduction policies with explicit, measurable trade-offs in bandwidth, latency, and user-visible stability.

\noindent\textbf{Fog data reduction (taxonomy + challenges).}
Sadri et al.\ present a systematic literature review of fog data reduction studies (2016--2022), organizing approaches and highlighting recurring objectives such as minimizing traffic while maintaining acceptable utility/quality \cite{sadri2022_fog_data_reduction_survey}. Their taxonomy supports our design choice to study practical reduction primitives (batching, compaction, and redundancy elimination) in a controlled end-to-end pipeline.

\noindent\textbf{Adaptive QoS and protocol-level control in publish/subscribe IoT.}
Palmese et al.\ propose a dynamic QoS controller for MQTT-SN that adapts to network conditions to improve performance in wireless sensor networks \cite{palmese2022_adaptive_qos_mqttsn}. While we use standard MQTT (not MQTT-SN), this work motivates our gateway-side adaptive publish-rate control: rather than fixing an update frequency, the gateway can adjust emission behavior based on observed publish health and backlog.

\noindent\textbf{MQTT performance and QoS trade-offs (including duplicates).}
Kovalchuk et al.\ study the impact of MQTT-based sensor network architectures and explicitly note that QoS~1 (``at least once'') may result in duplicate messages, while QoS~0 reduces overhead but does not guarantee delivery \cite{kovalchuk2018_mqtt_architecture_delay}. This directly informs our evaluation axis (QoS~0 vs.\ QoS~1) and motivates message-ID-based deduplication and within-batch compaction to prevent duplicate-induced overhead and UI instability.

\noindent\textbf{Freshness as a first-class metric.}
Yates et al.\ survey the Age of Information (AoI) literature and formalize ``age'' as a metric for the freshness of status updates observed at a monitor \cite{yates2021_age_of_information_survey}. We adopt this framing at the dashboard level by exposing an explicit age indicator and TTL-based staleness, enabling evaluation that goes beyond throughput/latency to quantify user-visible freshness under loss, jitter, and outages.

\noindent\textbf{Network emulation methodology with NetEm.}
Jurgelionis et al.\ empirically evaluate core NetEm functionalities and discuss practical considerations when using Linux-based emulation to stress test distributed systems \cite{jurgelionis2011_netem_empirical}. This supports our choice of deterministic, repeatable impairment profiles (loss, delay, jitter, duplication) as a sound methodology for comparing gateway variants under controlled degradations.

\noindent\textbf{Deterministic network emulation for repeatability.}
Garcia and Hurtig introduce KauNetEm, an extension of Linux NetEm that enables deterministic placement of emulation effects to improve repeatability in protocol evaluation \cite{garcia2016_kaunetem_netdev}. Although our implementation uses standard \texttt{tc netem}, their emphasis on determinism aligns with our scripted-phase design and motivates using fixed seeds and repeated trials per condition.
